### 2014-12-13 paper_20_sdo.tex
adding some new references

\subsection{WHAT IS SOFTWARE ENGINEERING?}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

@@

\begin{description}
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.
\end{description}

>>>>

\subsection{WHAT IS SOFTWARE ENGINEERING?}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

@@

\begin{description}
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

            ``
                A software defect is a bug or error that causes
                software to either stop operating or to produce
                invalid or unacceptable results.
            '' as quoted from
            \cite{Jones2009}.  Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
\end{description}

### 2014-12-13 paper_40_mpi.tex
adding some new references

The exact algorithm here is yet to be determined.

>>>>

\section{Schedule Adherence}
    \subsection{Overview}
        Delivery of software in a timely manner is an essential part of being a 
        successful SDO.  Being able to meet scheduled deadlines is a sign of accurate
        estimation and planning.  Drastically missing deadlines is a sign of an SDO
        with a process that needs refinement.  Studies have shown that 
        software projects exceed the estimates by an average of
        30\% \cite{Jorgensen2014}.  Thus it is important to score SDOs on accurate
        schedule adherence. Without tracking and measuring schedule adherence, it will
        not improve.

        The score is based upon the historical deviance of estimates for
        projects.  The top score of
        100 will be obtained when the schedule is met exactly.  A historical average 
        of deviance of schedule will be used to determine an appropriate range
        of schedule adherence.  A schedule that occurs within that range will be awarded
        a score of 0 or above, with less deviance being awarded more points.  Schedules
        that do not fall within the range of deviance will be awarded negative scores, 
        with a greater deviance resulting in a lower score all the way to -100 which means
        the package took twice as long as expected or more.
        For example, a package that takes more than twice as long to deliver than
        estimated will receive a score of -100.

    \newpage
    \subsection{Formula}

    The formula for schedule is based upon past performance.  Of the 422 projects
    scheduled since June 2013, only 45 projects had an estimated start date, estimated
    finish date and an actual finish date.  Of those 45 projects; 20 finished exactly on time,
    9 finished early and 16 finished late.

    The first step of the formula is finding the percentage the schedules were missed for 
    historical projects.  The calculation treats over- and under-estimating the schedule
    the same.  The same penalty is applied in both cases.  For example, being 15\% late
    will result in the same score as being 15\% early. Perform this calculation
    only for projects that did not exactly meet the estimated finish date.

        \begin{displaymath}
            \Delta_i = \left| \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1} \right|
        \end{displaymath}

        Find the average of the $\Delta_i$'s.  This is the average percent of a missed
        schedule.  
        \begin{displaymath}
           \bar{\Delta}  = \frac{\sum^n_{i=1}\Delta_i}{n}
        \end{displaymath}

        \textit{The formula for schedule is then a percentage above or below the $\Delta$.  
        The number is calculated for each project, and then averaged to form the schedule score.}

        After the $\bar{\Delta}$ is calculated, the following formulas are used to create the schedule scores
        for each project and then the averaged schedule score.

        \begin{displaymath}
           S_{4_i} = \left\{
             \begin{array}{lr}
                \text{where } \Delta_i \geq 1 & : -1 \times 100 \\
               \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times 100  \\
               \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times 100
             \end{array}
           \right] \text{   , calculate schedule score for each project $i$}
        \end{displaymath}

        \[
            S_{4} = \frac{\sum^n_{i=1} S_{4_i}}{n} \text{   , average the schedule scores}
        \]
        \begin{itemize}
            \item $n$ is the number of projects
            \item $F_{a_i}$ the actual finish date of project i
            \item $F_{s_i}$ the scheduled finish date of project i
            \item $B_{s_i}$ the scheduled beginning date of project i
            \item $\Delta_i$ the percent the schedule was missed
            \item $\bar{\Delta}$ is the average percent RT misses schedules, $\approx 26$
            \item $S_{4_i}$ is the schedule score for project $i$
        \end{itemize}

    \subsection{Example Calculation}
    \subsection{Data and Calculations}
    \subsubsection{Obtain the Data}
    \subsubsection{Run the Calculations}
    \subsection{Past Performance}
    \subsection{Process for the Future}
